### 2020-01-31 cv_models.tex
typo

\paragraph{Quality Metrics versus Reported Test Accuracies.}

@@

\paragraph{Layer Analytics: Correlation Flow in CV Models.}

@@

\paragraph{Layer Analytics: Behavior on Less Thoroughy Studied CV Models.}

>>>>

\paragraph{Coarse Analysis: Quality Metrics versus Reported Test Accuracies.}

@@

\paragraph{Layer Analysis: Correlation Flow in CV Models.}

@@

\paragraph{Layer Analysis: Behavior on Less Thoroughy Studied CV Models.}
